The Practical Application of MST

### 2021-02-17 article.Rmd
Graph of Cronbach's alpha

```{r}
library(ltm)

@@

# create a composite data frame and plot the alphas and the number of samples
# we'll want to focus on modules that show a low alpha and a small number of samples
# as we may want to get more trial data for these, or look at the items to make
# sure they are testing the right skill (or both)
module <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
alpha <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)

dfCronbachsAlpha <- data.frame(module, num_items, num_responses, alpha)

(dfCronbachsAlpha)
```
Ideally we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same ability.

>>>>

```{r Cronbach's alpha}
library(ltm)
library(ggrepel)

@@

# create a composite data frame and plot the alphas and the number of samples
# we'll want to focus on modules that show a low alpha and a small number of samples
# as we may want to get more trial data for these, or look at the items to make
# sure they are testing the right skill (or both)
module <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
stage <- c(1, 2, 2, 3, 3, 3, 3)
alpha <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)

dfCronbachsAlpha <- data.frame(module, stage, num_items, num_responses, alpha)

(dfCronbachsAlpha)

ggplot(dfCronbachsAlpha, aes(x=alpha, y=num_responses, size = num_items, color = module)) +
    geom_point() +
    geom_label_repel(aes(label = module, size = NULL)) +
    scale_x_continuous(limits = c(0, 1)) +
    theme(legend.position = "none") +
    labs(x = "alpha", y = "# responses")
```
Ideally we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same ability.
